%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
     { | Elmhurst, IL} % Location
    {Engineer II, Intern} % Organization
    {Mostardi-Platt} % Job title
    {May 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed software to mitigate human input, and facilitate the execution of Method 5 testing; effectively automating particulate testing.}
        \item {Integrated negative feedback control loop that implemented the automation software with small, motor-driven valves to further automate the totality of isokinetic air emissions testing.}
        \item {Designed and developed first networked particulate train to control vitals and receive real-time test data while up to 750 feet away.}
        \item {Implemented several API microservices in Node.js Koa and in the serverless AWS Lambda functions.}
        \item {Projected the advent of the aforementioned innovations could lead to a 11.5\% decrease in billable man-hours per year as well as an 22\% decrease in calculate test error.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
     { | Chicago, IL} % Location
    {Options Trading Automation Intern} % Organization
    {T.H. Brokerage} % Job title
    {May 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and deployed overall service infrastructure utilizing Docker container, CircleCI, and several AWS stack(Including EC2, ECS, Route 53, S3, CloudFront, RDS, ElastiCache, IAM), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway) companies in Hong Kong.}
        \item {Performed quantitative market analysis, and implemented ML algorithms to augment data collection effectiveness}
        \item {Deployed statistics and ML techniques to quantify opportunities and train models; evidence suggests the model yields a 63\% +/- 7.5\% accuracy rate predicting directional movements in S\&P 500 levels.}
      \end{cvitems}
    }

%---------------------------------------------------------
 
%---------------------------------------------------------
\end{cventries}
